---
title: "Portfolio Assessment: Performance and selling strategies"
output:
  html_document:
    df_print: paged
date: "`r Sys.Date()`"    
---


A timely retreat is a victory.



```{r echo=FALSE, message = FALSE, warning = FALSE}
# Set of libraries to use
library(YHFinR)
library(magrittr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(xts)
library(quantmod)


source('R/Plots.R')
source('R/StockResearchCore.R')
source('R/YahooFinanceUtils.R')

```

### Our portfolio`
```{r echo=FALSE, message = FALSE, warning = FALSE}
date <- gsub("-", "", today())
Portfolio.df <- data.frame(Ticker = c("UNA.AS", "DGV.MI", "VOW3.DE","PUM.DE",  "MC.PA", "CS.PA"),
                        nShares = c(100, 165, 50, 80, 14, 300),
                        AP = c(46, 30.5, 93, 55.40, 350, 16.10),
                        stringsAsFactors = FALSE)
```


```{r echo=FALSE, message = FALSE, warning = FALSE}
# Download daily historical data from today back to 5 years. 
# We take price adjusted by splits.
HistPrices.yahoo.list <- YHFinR::getYFHistPrices(Portfolio.df$Ticker, "5y", "1d")

```


```{r echo=FALSE, message = FALSE, warning = FALSE}
Portfolio.df <- Portfolio.df %>% 
  mutate(CP = sapply(HistPrices.yahoo.list, function(x) tail(x$adjclose, 1)),
         CV = nShares * CP,
         weight = CV / sum(CV)) %>% 
  arrange(desc(weight))

knitr::kable(Portfolio.df, caption = "Portfolio")

```

The Value of the current portfolio is `r sum(Portfolio.df$CV)`, allocated as follows.
```{r echo=FALSE, message = FALSE, warning = FALSE}
piechartplot(Portfolio.df)
```


### Factor 1: Quality

1. Healthy debts: A company shoud generate cash in order to repay its debt. The **Free Cash Flow to Debt** ratio is a good indicator of how quick a company pays back its debt. The lower this ratio the better.

FCF2D = $\frac{Debt}{Free Cash Flow}$

```{r echo=FALSE, message = FALSE, warning = FALSE}
Financials.list <- YHFinR::getYFFinancialsBasics(Portfolio.df$Ticker)
FCF.Debt.ROA.df <- rbind(
  sapply(Financials.list, function(x) .cleaNA_Neg(x$freeCashflow$raw)) , 
  sapply(Financials.list, function(x) .cleaNA_Neg(x$totalDebt$raw)),
  sapply(Financials.list, function(x) .cleaNA_Neg(x$returnOnAssets$raw))
  ) %>% 
  t() %>% 
  set_colnames(c("FCF", "Debt", "ROA")) %>% 
  as.data.frame() %>% 
  mutate(Ticker = rownames(.))

FCF.Debt.ROA.PF.df <- addPFavgFactor(FCF.Debt.ROA.df, Portfolio.df) %>% 
  mutate(FCF2D = .cleaNA_Neg(Debt / FCF))

FCF2D.df <- FCF.Debt.ROA.PF.df %>% 
  .[ , c("Ticker", "FCF2D")] 

barchartPFplot(FCF2D.df, "FCF2D")


```


2. Profitability: ROA 

```{r echo=FALSE, message = FALSE, warning = FALSE}
ROA.df <- FCF.Debt.ROA.PF.df %>% 
  .[ , c("Ticker", "ROA")] 

barchartPFplot(ROA.df, "ROA", labelPer = TRUE)

```

3. High Margin: We look for companies that generate free cash flow compare to its price. The **Free Cash Flow to Entreprise Value** ratio tells us how many years of cash flow would be needed to the return the 100% of the investment. Again, the lower, the better. Values bellow 1 would mean "free lunch".

FCF2EV = $\frac{EV}{Free Cash Flow}$

```{r echo=FALSE, message = FALSE, warning = FALSE}
EV <- sapply(YHFinR::getYFKeyStatistics(Portfolio.df$Ticker), function(x) x$enterpriseValue$raw) 
EV.df <- EV %>% 
  as.data.frame() %>% 
  set_colnames(c("EV")) %>% 
  mutate(Ticker = rownames(.)) %>% 
  addPFavgFactor(Portfolio.df)

FCF.Debt.EV.ROA.PF.df <- FCF.Debt.ROA.PF.df %>% 
  left_join(EV.df, by = "Ticker") %>% 
  mutate(FCF2EV = .cleaNA_Neg(EV / FCF))

FCF2EV.df <- FCF.Debt.EV.ROA.PF.df %>% 
  .[ , c("Ticker", "FCF2EV")] 

barchartPFplot(FCF2EV.df, "FCF2EV")

```

### Factor 2: Momentum 

Don't hold onto a stock simply because it is high quality. So called quality stocks have cycles too. Stan Weinstein (page 177)

Generic Intermediate-Term Momentum
Based on Gray-Vogel (page 80)


```{r echo=FALSE, message = FALSE, warning = FALSE}
HistPrices.yahoo.list[["STOXX50E"]] <- YHFinR::getYFHistPrices("^STOXX50E", "5y", "1d")$`^STOXX50E`
HistPrices.yahoo.xts.list <- lapply(HistPrices.yahoo.list, convertHistPr2xts)

Momentum.df <- sapply(HistPrices.yahoo.xts.list, calcGenericMomentum, term = 36, noise = 1) %>% 
  as.data.frame() %>% 
  set_colnames("Momentum") %>% 
  mutate(Ticker = rownames(.))

barchartPFplot(Momentum.df, VarName = "Momentum", PFTicker = "STOXX50E")


```

###  Factor 3: Timing Signal

Sell Signal - Pr < 1% SMA 30 weeks and slope negative (< 0.1)  
Hold Signal - No Sell  


```{r echo=FALSE, message = FALSE, warning = FALSE}
# From Daily to Weekly
HistPrices.wk.list <- sapply(HistPrices.yahoo.xts.list, daily2weekly)
# Add SMA30 & SMA30 Slope
HistPrices.wk.ma.list <- sapply(HistPrices.wk.list, addMA)
HistPrices.wk.ma.list <- sapply(HistPrices.wk.ma.list, addMASlope)

Signal.df <- sapply(HistPrices.wk.ma.list, function(obj, thresholdMA = 0.01, thresholdSlope = -0.2) {
  x <- tail(obj, 1)
  ifelse(x$adjclose < ((1 -thresholdMA) * x$MA) & x$MA.Slope < thresholdSlope, "SELL", "HOLD")
}) %>% 
  as.data.frame %>% 
  set_colnames("Signal") %>% 
  mutate(Ticker = rownames(.))

```

**StopLoss for the next month**  

Every month, we calculate a generic the StopLoss given a "Loss Threshold"" of 15% and "ProfitDropThreshold" of 20%.
In addition, there's an accurate StopLoss for those stocks with "hold" signal, of 5% of their MA. 


```{r echo=FALSE, message = FALSE, warning = FALSE}
# Accurated StopLoss
MA.df <- sapply(HistPrices.wk.ma.list, function(obj) tail(obj$MA, 1)) %>% 
  as.data.frame %>% 
  set_colnames("MA") %>% 
  mutate(Ticker = rownames(.))

StopLoss.dfä
<- Portfolio.df %>% 
  left_join(MA.df, by = "Ticker") %>% 
  calcStopLoss(LossThreshold = 0.15, ProfitDropThreshold = 0.2) %>% 
  .[ , c("Ticker", "PFStopLoss", "PrStopLoss", "StopLoss")]

```


###  Summary 
```{r echo=FALSE, message = FALSE, warning = FALSE}
# Quality
QualityRank <- FCF2D.df %>% 
  left_join(ROA.df, by = "Ticker") %>% 
  left_join(FCF2EV.df, by = "Ticker") %>%
  subset(Ticker != "PF") %>% 
  mutate(FCF2D = 1/ FCF2D,
         FCF2EV = 1 / FCF2EV) %>% 
  rankVariables(Rank.Name = "Quality", VarCols = c("FCF2D", "ROA","FCF2EV"))

# Quality
MomentumRank <- Momentum.df %>% 
  rankVariables(Rank.Name = "Momentum", VarCols = c("Momentum"))

# All together
FinalRank <- QualityRank %>% 
  left_join(MomentumRank, by = "Ticker") %>% 
  rankVariables(VarCols = c("Quality", "Momentum"), KeepVarCols = TRUE)

Summary <- Portfolio.df %>% 
  left_join(StopLoss.df, by = "Ticker") %>% 

  ol-{left_join(Signal.df, by = "Ticker") %>% 
  left_join(FinalRank, by = "Ticker") 

knitr::kable(
  Summary[ , c("Ticker", "AP", "CP", "weight", "StopLoss", "Signal", "Quality", "Momentum", "Final_rank")] %>%
    mutate(weight = round(weight, 4),
           StopLoss = round(StopLoss, 2)) %>% 
    arrange(desc(Final_rank)) 
  , caption = "Summary")

```


