---
title: "StockResearch"
author: "Gabriel Foix"
output:
  html_document:
    df_print: paged
date: "`r Sys.Date()`"
params:
  Ticker: Ticker
  Index: Index
  dump_file: dump_file

---

Buy Quality at the a good momentum and get rid of the fishy stocks on time. That's all.

```{r packages, echo=FALSE, message = FALSE, warning = FALSE}
# Set of libraries to use
library(YHFinR)
library(magrittr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(xts)
library(quantmod)


source('R/Plots.R')
source('R/StockResearchCore.R')
source('R/YahooFinanceUtils.R')

```

### Define candidates
```{r candidates, echo=FALSE, message = FALSE, warning = FALSE}
date <- gsub("-", "", today())
Candidates.df <- data.frame(Ticker = params$Ticker,
                        stringsAsFactors = FALSE)

Candidates_Ori <- nrow(Candidates.df)

```


Download all info needed applying the following filters:  

ROA > 1%  
FCF < 0  
PER > 0 and PER < 40  
History > 1 year 

```{r Financials_ROAfilter, echo = FALSE, message = FALSE, warning = FALSE}
Financials.list <- YHFinR::getYFFinancialsBasics(Candidates.df$Ticker)
# Save temp in case
remove("Financials.list.tmp.rds")
saveRDS(Financials.list, "Financials.list.tmp.rds")
# Financials.list <- readRDS("Financials.list.tmp.rds")

# Get ROA from Income Statement and BS when ROA is not informed.
lenROA <- sapply(Financials.list, function(x) length(x$returnOnAssets))
ROAnames <- names(lenROA[lenROA == 0])
DQNetIN <- YHFinR::getYFNetIncome(ROAnames) %>% 
  unlist()
DQTotAsset <- YHFinR::getYFTotalAssets(ROAnames) %>% 
  unlist()
idx <- match(names(DQNetIN), names(DQTotAsset))
DQROA <- DQNetIN[idx] / DQTotAsset[idx]

# Insert Fall-back returnOnAssets$raw
for (x in ROAnames) {
 Financials.list[[x]]$returnOnAssets$raw <- as.numeric(DQROA[x])
}

# Filter out ROA <= 0.01 
FilteredFinancials.list <- Financials.list[sapply(Financials.list, function(x) isTRUE(x$returnOnAssets$raw > 0.01))]

# Reduce candidates
Candidates.df <- Candidates.df[Candidates.df$Ticker %in% names(FilteredFinancials.list),, drop = FALSE]
Candidates_ROA <- nrow(Candidates.df)

```

### Factor 1: Quality

1. Healthy debts: A company shoud generate cash in order to repay its debt. The **Free Cash Flow to Debt** ratio is a good indicator of how quick a company pays back its debt. The lower this ratio the better.

FCF2D = $\frac{Debt}{Free Cash Flow}$

```{r FCF2D, echo=FALSE, message = FALSE, warning = FALSE}
# Using the Current Candidates
FilteredFinancials.list <- FilteredFinancials.list[names(FilteredFinancials.list) %in% Candidates.df$Ticker]

# Get FCF from CashFlow as fallback when FCF is negative or zero
FCF <- sapply(FilteredFinancials.list, function(x) .cleaNA_Neg(x$freeCashflow$raw))
DQFCF <- YHFinR::getYFFreeCashFlow(names(FCF[FCF <= 0])) %>% 
  unlist()
FCF[match(names(DQFCF), names(FCF))] <- .cleaNA_Neg(DQFCF)

FCF.Debt.ROA.df <- rbind(
  FCF, 
  sapply(FilteredFinancials.list, function(x) .cleaNA_Neg(x$totalDebt$raw)),
  sapply(FilteredFinancials.list, function(x) .cleaNA_Neg(x$returnOnAssets$raw, rplneg = 0))
  ) %>% 
  t() %>% 
  set_colnames(c("FCF", "Debt", "ROA")) %>% 
  as.data.frame() %>% 
  mutate(Ticker = rownames(.),
         FCF2D = .cleaNA_Neg(Debt / FCF, rplneg = 99))


FCF2D.df <- FCF.Debt.ROA.df %>% 
  .[ , c("Ticker", "FCF2D")] 

barchartPFplot(FCF2D.df, "FCF2D", theHighertheBetter = FALSE, PFequallyweigthed = TRUE)


```


2. Profitability: ROA 

```{r ROA, echo=FALSE, message = FALSE, warning = FALSE}
ROA.df <- FCF.Debt.ROA.df %>% 
  .[ , c("Ticker", "ROA")] 

barchartPFplot(ROA.df, "ROA", PFequallyweigthed = TRUE, labelPer = TRUE)

```

3. High Margin: We look for companies that generate free cash flow compare to its price. The **Free Cash Flow to Entreprise Value** ratio tells us how many years of cash flow would be needed to the return the 100% of the investment. Again, the lower, the better. Values bellow 1 would mean "free lunch".

FCF2EV = $\frac{EV}{Free Cash Flow}$

```{r FCF2EV, echo=FALSE, message = FALSE, warning = FALSE}
# Reduce Candidates by filtering FCF > 0
Candidates.df <- Candidates.df[Candidates.df$Ticker %in% names(FCF)[FCF>0],, drop = FALSE]
Candidates_FCF <- nrow(Candidates.df)

KeyStatistics.list <- YHFinR::getYFKeyStatistics(Candidates.df$Ticker)

# Save temp in case
remove("KeyStatistics.list.tmp.rds")
saveRDS(KeyStatistics.list, "KeyStatistics.list.tmp.rds")
# KeyStatistics.list <- readRDS("KeyStatistics.list.tmp.rds")

EV <- sapply(KeyStatistics.list, function(x) x$enterpriseValue$raw)

EV.df <- unlist(EV[sapply(EV, is.numeric)]) %>% 
  .SRformat(c("EV"))

FCF.Debt.EV.ROA.df <- FCF.Debt.ROA.df %>% 
  left_join(EV.df, by = "Ticker") %>% 
  mutate(FCF2EV = .cleaNA_Neg(EV / FCF, rplneg = 99))

FCF2EV.df <- FCF.Debt.EV.ROA.df %>% 
  .[ , c("Ticker", "FCF2EV")] 

barchartPFplot(FCF2EV.df, "FCF2EV", theHighertheBetter = FALSE, PFequallyweigthed = TRUE)

```

#### Download Historical Data
Download only stocks not filtered previously

```{r HisPrices, echo=FALSE, message = FALSE, warning = FALSE}
# Download daily historical data from today back to 5 years. 
# We take price adjusted by splits.
HistPrices.yahoo.list <- YHFinR::getYFHistPrices(Candidates.df$Ticker, "5y", "1d")

# Filter out NULLs, NAs & hist < 1 year
HistPrices.yahoo.list <- HistPrices.yahoo.list[!sapply(HistPrices.yahoo.list, is.null)]
HistPrices.yahoo.list <- cleanNArows(HistPrices.yahoo.list)
HistPrices.yahoo.list <- HistPrices.yahoo.list[sapply(HistPrices.yahoo.list, nrow) > 252]

# Save temp in case
remove("HistPrices.yahoo.list.tmp.rds")
saveRDS(HistPrices.yahoo.list, "HistPrices.yahoo.list.tmp.rds")

# After that, reduce candidates
Candidates.df <- Candidates.df[Candidates.df$Ticker %in% names(HistPrices.yahoo.list),, drop = FALSE]
Candidates_Hist <- nrow(Candidates.df)

```

### Value touch  
Filter out stocks with PER > 40

```{r PER, echo=FALSE, message = FALSE, warning = FALSE}
EPS <- sapply(KeyStatistics.list, function(x) x$trailingEps$raw)
CP <- sapply(HistPrices.yahoo.list, function(x) tail(x$adjclose, 1))

PER.df <- unlist(EPS[sapply(EPS, is.numeric)]) %>% 
  .SRformat(c("EPS")) %>% 
  left_join(unlist(CP[sapply(CP, is.numeric)]) %>% 
  .SRformat(c("CP")), 
  by = "Ticker") %>% 
  mutate(PER = .cleanNAs(CP / EPS)) %>% 
  .[c("Ticker", "PER")]

# Reduce Candidates after PER filter
Candidates.df <- Candidates.df[Candidates.df$Ticker %in% subset(PER.df, PER > 0 & PER < 40)$Ticker,, drop = FALSE]
Candidates_PER <- nrow(Candidates.df)

```


Report Candidates
```{r ReportCandidates, echo=FALSE, message = FALSE, warning = FALSE}

FilterSummary <- data.frame(Filter = c("Initial", "ROA", "FCF", "Hist1Y", "PER"),
                            NStocks = c(Candidates_Ori, Candidates_ROA, Candidates_FCF,  Candidates_Hist, Candidates_PER),
                            stringsAsFactors = FALSE)

knitr::kable( FilterSummary,
              caption = "Filter Summary")

```


### Factor 2: Momentum 

Don't hold onto a stock simply because it is high quality. So called quality stocks have cycles too. Stan Weinstein (page 177)

Generic Intermediate-Term Momentum
Based on Gray-Vogel (page 80)


```{r Momentum, echo=FALSE, message = FALSE, warning = FALSE}
HistPrices.yahoo.list[["Index"]] <- YHFinR::getYFHistPrices(params$Index, "5y", "1d")$Index
HistPrices.yahoo.xts.list <- lapply(HistPrices.yahoo.list, convertHistPr2xts)

Momentum.df <- sapply(HistPrices.yahoo.xts.list, calcGenericMomentum, term = 36, noise = 1) %>% 
  .SRformat("Momentum")

barchartPFplot(Momentum.df, VarName = "Momentum", PFTicker = "Index")


```

###  Factor 3: Timing Signal

Sell Signal - Pr < 1% SMA 30 weeks and slope negative (< -0.2)  
Buy Signal -  109% * SMA30 < Pr > SMA 30 and slope positive (> 0.2)  
Hold Signal - Neither Buy nor Sell  


```{r Signal, echo=FALSE, message = FALSE, warning = FALSE}
# From Daily to Weekly
HistPrices.wk.list <- lapply(HistPrices.yahoo.xts.list, daily2weekly)
# Add SMA30 & SMA30 Slope
HistPrices.wk.ma.list <- lapply(HistPrices.wk.list, addMA)
HistPrices.wk.ma.list <- lapply(HistPrices.wk.ma.list, addMASlope)

Signal.df <- sapply(HistPrices.wk.ma.list, function(obj, thresholdMA_SELL = 0.01, thresholdMA_BUY = 0.09,  thresholdSlope_SELL = -0.2, thresholdSlope_BUY = 0.2) {
  x <- tail(obj, 1)
  ifelse(x$adjclose < ((1 -thresholdMA_SELL) * x$MA) & x$MA.Slope < thresholdSlope_SELL, "SELL", 
         ifelse(x$adjclose < ((1 + thresholdMA_BUY) * x$MA) & x$adjclose > x$MA & x$MA.Slope > thresholdSlope_BUY, "BUY", "HOLD"))
}) %>%
  .SRformat("Signal")

```

#### Calc Market Cap  
Using free float shares
```{r MarketCap, echo=FALSE, message = FALSE, warning = FALSE}
NShares <- sapply(KeyStatistics.list, function(x) x$floatShares$raw)

MCap.df <- unlist(NShares[sapply(NShares, is.numeric)]) %>% 
  .SRformat(c("NShares")) %>% 
  left_join(unlist(CP[sapply(CP, is.numeric)]) %>% 
  .SRformat(c("CP")), 
  by = "Ticker") %>% 
  mutate(MCap = .cleanNAs(CP * NShares)) %>% 
  .[c("Ticker", "MCap")]

```



###  Summary 
```{r Summary, echo=FALSE, message = FALSE, warning = FALSE}
# Quality
QualityRank <- FCF2D.df %>% 
  left_join(ROA.df, by = "Ticker") %>% 
  left_join(FCF2EV.df, by = "Ticker") %>%
  subset(Ticker != "PF") %>% 
  mutate(FCF2D = 1/ FCF2D,
         FCF2EV = 1 / FCF2EV) %>% 
  rankVariables(Rank.Name = "Quality", VarCols = c("FCF2D", "ROA","FCF2EV"))

# Momentum
MomentumRank <- Momentum.df %>% 
  rankVariables(Rank.Name = "Momentum", VarCols = c("Momentum"))

# All together
FinalRank <- QualityRank %>% 
  left_join(MomentumRank, by = "Ticker") %>% 
  rankVariables(VarCols = c("Quality", "Momentum"), KeepVarCols = TRUE)


Summary <- Candidates.df %>%
  left_join(Signal.df, by = "Ticker") %>% 
  left_join(FinalRank, by = "Ticker") %>% 
  left_join(PER.df, by = "Ticker") %>% 
  left_join(MCap.df, by = "Ticker")

knitr::kable(
  subset(Summary, PER < 40, c("Ticker", "Signal", "Quality", "Momentum", "Final_rank", "PER", "MCap")) %>% 
  arrange(desc(Final_rank)),
  caption = "Summary")

```


Save output in template
```{r Report, echo=FALSE, message = FALSE, warning = FALSE}

Dump <- Summary %>%
  left_join(ROA.df, by = "Ticker") %>% 
  left_join(FCF2EV.df, by = "Ticker") %>%
  left_join(FCF2D.df, by = "Ticker") %>% 
  left_join(Momentum.df %>% 
              rename(MomentumValue = Momentum), by = "Ticker") %>% 
  arrange(desc(Final_rank))

write.csv(Dump, params$dump_file, row.names = FALSE)
  
```

