---
title: "Adding an extra stock into a portfolio"
output:
  html_document:
    df_print: paged
---

Equity research based on the following preconditions and factors.
* European stocks: DE, FR, BE, NL, ES, IT, PO
* Market capitalization > 1000MM
* At least 5 years of history

**Factor 1: Value**
PER, priceToBook, EBITDA / Enterprise Value

**Factor 2: Profitability**
Return on Equity, Operating Margin

**Factor 3: Balance Sheet**
Current Ratio, Total Cash Per Share / Price

**Factor 6: Dividend**
Trailing Annual Dividend Yield * (1 - Payout Ratio)

**Factor 4: Growth**
Quarterly Revenue Growth
Quarterly Earnings Growth

**Factor 5: Momentum**
52-Week Change
52-Week Change - S&P500 52-Week Change
PerOver50MA
PerOver200MA
PerOverAnMin
PerOverAnMax


Set of libraries to use
```{r message = FALSE, warning = FALSE}
library(magrittr)
library(jsonlite)
library(lubridate)
library(dplyr)
library(quantmod)
library(XML)
library(ggplot2)

source('~/GitHub/StockSystems/YahooFinanceUtils.R')
source('~/GitHub/StockSystems/Plots.R')
source('~/GitHub/StockSystems/StockResearchCore.R')

```


Defining our portfolio
```{r}
Portfolio.df <- data.frame(Tickers = c("UNA.AS", "TGYM.MI", "VOW3.DE","PUM.DE",  "MC.PA", "CS.PA", "REE.MC"),
                        nShares = c(100, 650, 50, 80, 14, 300, 425),
                        AP = c(46, 7, 93, 55.40, 350, 16.10, 17.20),
                        stringsAsFactors = FALSE)
```

```{r echo = FALSE}
nyearsback <- 10
```

Download daily historical data from today back to `r nyearsback` years. 
We take price adjusted by splits.

```{r message = FALSE, warning = FALSE}
start_date = Sys.Date() - lubridate::years(nyearsback)
HistPrices.yahoo.list <- getHistPriceYF(Portfolio.df$Tickers, "w", start_date)
```

HistPrices.yahoo.list is a list of `r ncol(Portfolio.df)` elements, one per each component of the portfolio.

WE calculate first the StopLoss given a "Loss Threshold"" of 15% and "ProfitDropThreshold" of 20%.
rom here, we get the value and allocation of the current portfolio. 

```{r echo=FALSE}
Portfolio.df <- Portfolio.df %>% 
  mutate(CP = sapply(HistPrices.yahoo.list, tail, 1)) %>% 
  calcStopLoss(LossThreshold = 0.15, ProfitDropThreshold = 0.2)

Portfolio.df[, c("Tickers", "AP", "CP", "StopLoss")]

```

Value of the current portfolio is `r sum(CurrentAlloc.df$Value)`, allocated as follows.

```{r echo=FALSE}

Portfolio.df <- Portfolio.df %>% 
    dplyr::mutate(weight = CV / sum(CV)) %>% 
  arrange(desc(weight))

Portfolio.df[, c("Tickers", "CV", "weight")]


```

```{r}



piechartplot(Portfolio.df)

```


Download fundamentals from [Yahoo Finance](https://finance.yahoo.com/) as of `r today()` and build an homogeneus indicator of each of our 5 factors.

```{r message = TRUE, warning = FALSE}
FinRatios <- getFinRatios(Portfolio.df$Tickers) %>% 
  mutate(Date = date)
```

**Pre-condition: Liquidity: Market Cap**
All companies in our portfolio should have a Market Cap > 1000MM (1B in Yahoo Finance convertion)

```{r echo=FALSE}

MarketCap.df <- getMarketCap(FinRatios) %>% 
  addPFavgFactor(CurrentAlloc.df) %>% 
  arrange(desc(MarketCap)) 

barchartPFplot(MarketCap.df, "MarketCap")

```

