---
title: "Adding an extra stock into a portfolio"
output:
  html_document:
    df_print: paged
---

Equity research based on the following preconditions and factors.
* European stocks: DE, FR, BE, NL, ES, IT, PO
* Market capitalization > 1000MM
* At least 5 years of history

**Factor 1: Value**
PER, priceToBook, EBITDA / Enterprise Value

**Factor 2: Profitability**
Return on Equity, Operating Margin

**Factor 3: Balance Sheet**
Current Ratio, Total Cash Per Share / Price

**Factor 6: Dividend**
Trailing Annual Dividend Yield * (1 - Payout Ratio)

**Factor 4: Growth**
Quarterly Revenue Growth
Quarterly Earnings Growth

**Factor 5: Momentum**
52-Week Change
52-Week Change - S&P500 52-Week Change
PerOver50MA
PerOver200MA
PerOverAnMin
PerOverAnMax


Set of libraries to use
```{r message = FALSE, warning = FALSE}
library(magrittr)
library(jsonlite)
library(lubridate)
library(dplyr)
library(quantmod)
library(XML)
library(ggplot2)

source('~/GitHub/StockSystems/YahooFinanceUtils.R')
source('~/GitHub/StockSystems/Plots.R')
source('~/GitHub/StockSystems/StockResearchCore.R')

```


Defining our portfolio
```{r}
Portfolio.df <- data.frame(Tickers = c("UNA.AS", "TGYM.MI", "VOW3.DE","PUM.DE",  "MC.PA", "CS.PA", "REE.MC"),
                        nShares = c(100, 650, 50, 80, 14, 300, 425),
                        AP = c(46, 7, 93, 55.40, 350, 16.10, 17.20),
                        stringsAsFactors = FALSE)
```

```{r echo = FALSE}
nyearsback <- 10
```

Download daily historical data from today back to `r nyearsback` years. 
We take price adjusted by splits.

```{r message = FALSE, warning = FALSE}
start_date = Sys.Date() - lubridate::years(nyearsback)
HistPrices.yahoo.list <- getHistPriceYF(Portfolio.df$Tickers, "w", start_date)
```

HistPrices.yahoo.list is a list of `r ncol(Portfolio.df)` elements, one per each component of the portfolio.

WE calculate first the StopLoss given a "Loss Threshold"" of 15% and "ProfitDropThreshold" of 20%.
rom here, we get the value and allocation of the current portfolio. 

```{r echo=FALSE}
Portfolio.df <- Portfolio.df %>% 
  mutate(CP = sapply(HistPrices.yahoo.list, tail, 1)) %>% 
  calcStopLoss(LossThreshold = 0.15, ProfitDropThreshold = 0.2)

Portfolio.df[, c("Tickers", "AP", "CP", "StopLoss")]

```

Value of the current portfolio is `r sum(CurrentAlloc.df$Value)`, allocated as follows.

```{r echo=FALSE}

Portfolio.df <- Portfolio.df %>% 
    dplyr::mutate(weight = CV / sum(CV)) %>% 
  arrange(desc(weight))

Portfolio.df[, c("Tickers", "CV", "weight")]


```

```{r}



piechartplot(Portfolio.df)

```


Download fundamentals from [Yahoo Finance](https://finance.yahoo.com/) as of `r today()` and build an homogeneus indicator of each of our 5 factors.

```{r message = TRUE, warning = FALSE}
FinRatios <- getFinRatios(Portfolio.df$Tickers) %>% 
  mutate(Date = date)
```

**Pre-condition: Liquidity: Market Cap**
All companies in our portfolio should have a Market Cap > 1000MM (1B in Yahoo Finance convertion)

```{r echo=FALSE}

MarketCap.df <- getMarketCap(FinRatios) %>% 
  addPFavgFactor(CurrentAlloc.df) %>% 
  arrange(desc(MarketCap)) 

barchartPFplot(MarketCap.df, "MarketCap")

```

** Factor 1: Quality **

Quality stocks are defined as stocks that meet the following four criteria:

Profitability, which includes such measures as gross profits over assets, return on equity, return on assets, and cash flows over assets.
Growth, which is defined as stocks that exhibit high growth on the above-mentioned profitability criteria.
Risk, which includes stocks with low market beta, volatility, and leverage.
Payout, which includes stocks with higher payouts through dividends and/or buybacks.
What define the quality of a company? A quality company to invest in needs to have a good balance of these 3 elements. 

1. Healthy debts: A company shoud generate cash in order to repay its debt. The **Free Cash Flow to Debt** ratio is a good indicator of how quick a company pays back its debt. The lower this ratio the better.

FCF2D = $\frac{Debt}{Free Cash Flow}$

2. Profitability: Both ROA and return on equity (ROE) are measures of how a company utilizes its resources. Essentially, ROE only measures the return on a company’s equity, leaving out the liabilities. Thus, ROA accounts for a company’s debt and ROE does not. The more leverage and debt a company takes on, the higher ROE will be relative to ROA. 

3. Payout: Companies that are committed to reward investors through dividends.
Trailing Annual Dividend Yield
5 Year Average Dividend Yield
Payout Ratio 

